Research paper

### 2012-11-04 Research paper.tex
More fancy intro

In this paper, I will give a detailed overview of the research project Colibri. Colibri, carried out a the Radboud University Nijmegen by Maarten van Gompel and Antal van den Bosch, investigates the identification and extraction of constructions in natural language, and the usage of such constructions in Machine Translation. These constructions can be a various lengths, and, importantly, can also contain one or more gaps. The constructions are not identified on the basis of explicit 'human' knowledge about language and grammar ('linguistic theory'), but are distilled from large amounts of text ('text corpora') with the help of context-sensitive machine-learning techniques.

@@

@@

\section{Theoretical framework}
\section{Achievements so far}
\section{Main outstanding questions}
\section{Strengths and weaknesses}
\section{Possibilities for future research}
\section{Conclusion}
\end{document}

>>>>

When one of Starfleet's vessels meets an alien ship in areas where no man has gone before, they can (almost) always communicate with these aliens (almost) instantly; they speak to them in English, and these aliens answer in English. This is possible because, according to the Star Trek lore, the protagonists make use of a so-called Universal Translator. This Universal Translator can (1) recognize speech in every language, (2) translate what it has 'heard' to any other language, (3) make its results audible with speech synthesis and (4) learn itself new languages when needed. Unfortunately, like many technologies in Star Trek, this is far from reality: there have been various attempts at the first three tasks in particular, but no software currently in existence can do this as perfect as the Universal Translator. \\\indent
In this paper, I will give a detailed overview of the research project Colibri, which basically is an attempt to improve the technology needed for the second task: automatically translating text from one language to another. More specifically, the project investigates the identification and extraction of constructions in natural language, and how these can be used in Machine Translation. These constructions can be a various lengths, and, importantly, can also contain one or more gaps. The constructions are not identified on the basis of explicit 'human' knowledge about language and grammar ('linguistic theory'), but are distilled from large amounts of text ('text corpora') with the help of context-sensitive machine-learning techniques.

@@

\section{Theoretical framework}

@@

\section{Achievements so far}
\section{Main outstanding questions}
\section{Strengths and weaknesses}
\section{Possibilities for future research}
\section{Conclusion}
\end{document}
